### 2018-10-10 doc/plos/text/manuscript.tex
discuss relative inaccuracy in hhs2

@@

TODO(why is hhs2 the worst? PR/VI: least ground truth, extreme noise, disparate
dynamics, no sensors other than sar3; NY, JFK: inferred.)

>>>>

There are several challenges specific to nowcasting in HHS2 and Census region
two. First, the constituent territories Puerto Rico (PR) and the US Virgin
Islands (VI) have limited ground truth---far fewer observations than all other
locations. Second, the only sensor currently available for each of New York
\textit{excluding New York City}, PR, and VI is SAR3---a time-series model
which incorporates no real-world measurements. Finally, the epidemiological
dynamics (timing, strain distribution, etc.) within HHS2 are disparate; New
Jersey and New York (including New York City) form one epidemiological cluster
while PI and VI form another.

@@
